Opening up the court (surface) in tennis grand slams

### 2020-08-02 paper_results/EDA/graphics_eda.Rmd
more graph updates WOO

```{r}
spain_wins <- filter(gs_players_v2, ioc == "ESP", round < "QF") %>% 
  group_by(tournament, round) %>% 
  dplyr::summarise(win_prop = mean(did_win, na.rm=TRUE),
            win_prop_se = sqrt(win_prop*(1-win_prop)/n()),
            avg_ranking = mean(rank),
            rank_se = sd(rank)/sqrt(n()),
            n_size = n())

@@

@@

p_atp_percent <- atp_ace_ht %>% # could also try median
ggplot( aes(ht, med_ace_perc)) + 
  geom_jitter(size=1.5, width = 0.8) + 
  geom_smooth( method = "lm", color="black") + 
  geom_label_repel(data=dplyr::filter(atp_ace_ht, name %in% atp_servers),
            aes(ht, med_ace_perc, label=name),
            alpha=.8, seed=1234, show.legend=FALSE, size = 6,
            nudge_y = c(-.025, 0, 0, -0.05,0.02),
            nudge_x = c(6, -2, -2, -3, -1)) +
  geom_label_repel(data=dplyr::filter(atp_ace_ht, name %in% atp_servers),
            aes(ht, med_ace_perc, label = name),
            seed=1234, fill=NA, show.legend=FALSE, size = 6,
            nudge_y = c(-.025, 0, 0, -0.05,0.02),
            nudge_x = c(6, -2, -2, -3, -1)) +
  labs(x = "Height in cm", y = "Median ace% per match", title = "ATP") +
  my_theme 
# + 
#   ylim(c(0, 0.25))
p_atp_percent

p_wta_percent <- wta_ace_ht %>% # could also try median
ggplot( aes(ht, med_ace_perc)) + 
  geom_jitter(size=1.5, width=.6) + 
  geom_smooth( method = "lm", color="black") + 
  geom_label_repel(data=dplyr::filter(wta_ace_ht, name %in% wta_servers),
            aes(ht, med_ace_perc, label=name),
            alpha=.8, seed=1234, show.legend=FALSE, size = 6,
            nudge_y = c(-.02, .01, 0.01, -0.01, -0.02 ),
            nudge_x = c(-3, 5, -3, 0, 0)) + 
  geom_label_repel(data=dplyr::filter(wta_ace_ht, name %in% wta_servers),
            aes(ht, med_ace_perc, label = name),
            seed=1234, fill=NA, show.legend=FALSE, size = 6,
            nudge_y = c(-.02, .01, 0.01, -0.01, -0.02 ),
            nudge_x = c(-3, 5, -3, 0, 0)) +
  labs(x = "Height in cm", y = "Median ace% per match", title = "WTA") +
  my_theme
# + 
#   ylim(c(0, 0.25))

@@

p_wta_percent <- wta_ace_ht %>% # could also try median
ggplot( aes(ht, med_ace_perc)) + 
  geom_jitter(size=1.5, width = 0.6) + 
  geom_smooth( method = "lm", color="black") + 
  geom_label_repel(data=dplyr::filter(wta_ace_ht, name %in% wta_servers),
            aes(ht, med_ace_perc, label=name),
            alpha=.8, seed=1234, show.legend=FALSE, size = 5,
            nudge_y = c(-.02, .01, 0.01, -0.01, -0.02 ),
            nudge_x = c(-1, 5, 5, 0, 0)) + 
  geom_label_repel(data=dplyr::filter(wta_ace_ht, name %in% wta_servers),
            aes(ht, med_ace_perc, label = name),
            seed=1234, fill=NA, show.legend=FALSE, size = 5,
            nudge_y = c(-.02, .01, 0.01, -0.01, -0.02 ),
            nudge_x = c(-1, 5, 5, 0, 0)) +
  labs(x = "Height in cm", y = " ", title = "WTA") +
  my_theme +
  ylim(c(0, 0.25))

@@

>>>>

```{r}
spain_wins <- filter(gs_players_v2, ioc == "ESP", round < "QF") %>% 
  group_by(tournament, round) %>% 
  dplyr::summarise(win_prop = mean(did_win, na.rm=TRUE),
            win_prop_se = sqrt(win_prop*(1-win_prop)/n()),
            avg_ranking = mean(rank),
            rank_se = sd(rank)/sqrt(n()),
            n_size = n(),
            med_ranking = median(rank, na.rm = TRUE))

@@

ggplot(spain_wins, aes(round, med_ranking, color=tournament, group=tournament, fill = tournament)) + 
  geom_line(size=3) + 
  labs(title = "Median ranking among Spaniards",
       x = " ",
       y = "Median rank") + 
  scale_color_manual(" ", values=tournament_colors,
                                labels = c("Australian Open\n(Plexicushion)",
                                           "French Open\n(Clay)",
                                           "US Open\n(DecoTurf)",
                                           "Wimbledon\n(Grass)")) + my_theme +
  guides(color = guide_legend(override.aes = list(size = 7)))

@@

p_atp_percent <- atp_ace_ht %>% # could also try median
ggplot( aes(ht, med_ace_perc)) + 
  geom_jitter(size=1.5, width = 0.8) + 
  geom_smooth( method = "lm", color="black") + 
  geom_label_repel(data=dplyr::filter(atp_ace_ht, name %in% atp_servers),
            aes(ht, med_ace_perc, label=name),
            alpha=.8, seed=1234, show.legend=FALSE, size = 6,
            nudge_y = c(-.025, 0, -.01, -0.05,0.02),
            nudge_x = c(6, -2, 0, -3, -1)) +
  geom_label_repel(data=dplyr::filter(atp_ace_ht, name %in% atp_servers),
            aes(ht, med_ace_perc, label = name),
            seed=1234, fill=NA, show.legend=FALSE, size = 6,
            nudge_y = c(-.025, 0, -0.01, -0.05,0.02),
            nudge_x = c(6, -2, 0, -3, -1)) +
  labs(x = "Height in cm", y = "Median ace% per match", title = "ATP") +
  my_theme 
# + 
#   ylim(c(0, 0.25))
p_atp_percent

p_wta_percent <- wta_ace_ht %>% # could also try median
ggplot( aes(ht, med_ace_perc)) + 
  geom_jitter(size=1.5, width=.6) + 
  geom_smooth( method = "lm", color="black") + 
  geom_label_repel(data=dplyr::filter(wta_ace_ht, name %in% wta_servers),
            aes(ht, med_ace_perc, label=name),
            alpha=.8, seed=1234, show.legend=FALSE, size = 6,
            nudge_y = c(-.02, .01, 0.01, -0.01, -0.03 ),
            nudge_x = c(-3, 5, -3, 0, 0)) + 
  geom_label_repel(data=dplyr::filter(wta_ace_ht, name %in% wta_servers),
            aes(ht, med_ace_perc, label = name),
            seed=1234, fill=NA, show.legend=FALSE, size = 6,
            nudge_y = c(-.02, .01, 0.01, -0.01, -0.03 ),
            nudge_x = c(-3, 5, -3, 0, 0)) +
  labs(x = "Height in cm", y = "Median ace% per match", title = "WTA") +
  my_theme
# + 
#   ylim(c(0, 0.25))

@@

p_wta_percent <- wta_ace_ht %>% # could also try median
ggplot( aes(ht, med_ace_perc)) + 
  geom_jitter(size=1.5, width = 0.6) + 
  geom_smooth( method = "lm", color="black") + 
  geom_label_repel(data=dplyr::filter(wta_ace_ht, name %in% wta_servers),
            aes(ht, med_ace_perc, label=name),
            alpha=.8, seed=1234, show.legend=FALSE, size = 5,
            nudge_y = c(-.02, .01, 0.01, -0.01, -0.01),
            nudge_x = c(-1, 5, 5, 0, 0)) + 
  geom_label_repel(data=dplyr::filter(wta_ace_ht, name %in% wta_servers),
            aes(ht, med_ace_perc, label = name),
            seed=1234, fill=NA, show.legend=FALSE, size = 5,
            nudge_y = c(-.02, .01, 0.01, -0.01, -0.01),
            nudge_x = c(-1, 5, 5, 0, 0)) +
  labs(x = "Height in cm", y = " ", title = "WTA") +
  my_theme +
  ylim(c(0, 0.25))

@@

p_atp_percent <- atp_ace_ht %>% # could also try median
ggplot( aes(ht, avg_ave_perc)) + 
  geom_jitter(size=1.5, width = 0.8) + 
  geom_smooth( method = "lm", color="black") + 
  geom_label_repel(data=dplyr::filter(atp_ace_ht, name %in% atp_servers),
            aes(ht, avg_ave_perc, label=name),
            alpha=.8, seed=1234, show.legend=FALSE, size = 6,
            nudge_y = c(-.025, 0, -.01, -0.05,0.02),
            nudge_x = c(6, -2, 0, -3, -1)) +
  geom_label_repel(data=dplyr::filter(atp_ace_ht, name %in% atp_servers),
            aes(ht, avg_ave_perc, label = name),
            seed=1234, fill=NA, show.legend=FALSE, size = 6,
            nudge_y = c(-.025, 0, -0.01, -0.05,0.02),
            nudge_x = c(6, -2, 0, -3, -1)) +
  labs(x = "Height in cm", y = "Mean ace% per match", title = "ATP") +
  my_theme 
# + 
#   ylim(c(0, 0.25))
p_atp_percent

p_wta_percent <- wta_ace_ht %>% # could also try median
ggplot( aes(ht, avg_ave_perc)) + 
  geom_jitter(size=1.5, width=.6) + 
  geom_smooth( method = "lm", color="black") + 
  geom_label_repel(data=dplyr::filter(wta_ace_ht, name %in% wta_servers),
            aes(ht, avg_ave_perc, label=name),
            alpha=.8, seed=1234, show.legend=FALSE, size = 6,
            nudge_y = c(-.02, .01, 0.01, -0.01, -0.03 ),
            nudge_x = c(-3, 5, -3, 0, 0)) + 
  geom_label_repel(data=dplyr::filter(wta_ace_ht, name %in% wta_servers),
            aes(ht, avg_ave_perc, label = name),
            seed=1234, fill=NA, show.legend=FALSE, size = 6,
            nudge_y = c(-.02, .01, 0.01, -0.01, -0.03 ),
            nudge_x = c(-3, 5, -3, 0, 0)) +
  labs(x = "Height in cm", y = "Mean ace% per match", title = "WTA") +
  my_theme
# + 
#   ylim(c(0, 0.25))

if(save_graph){
ggsave("../plots/aces_mean_percent_v2.jpg", height=8, width=graphic_width_long)
}
